Exploring probability distributions for bivariate temporal granularities

### 2019-08-05 main.Rmd
adding section on computation

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold', 
  cache = FALSE, cache.path = 'cache/', 
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE}
#read_chunk('scripts/main.R')
```

```{r load}
```

@@

For example, suppose the time index is in minutes, and let $n_i$ be the number of categories created by $C_i$. Then the following categorizations can be computed.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
MOH: & $C_1(s)$ & $= s \mod 60$ & $n_1 =$&$60$ \\
MOD: & $C_2(s)$ & $= s \mod `r 60*24`$ & $n_2=$&$`r 60*24`$\\
MOW: & $C_3(s)$ & $= s \mod `r 60*24*7`$ & $n_2=$&$`r 60*24*7`$\\
HOD: & $C_4(s)$ & $= \lfloor s/60\rfloor\mod 24$  & $n_4 =$&$24$ \\
HOW: & $C_6(s)$ & $= \lfloor s/60\rfloor\mod 24*7$  & $n_5=$&$`r 24*7`$\\
DOW: & $C_7(s)$ & $= \lfloor s/24*60\rfloor \mod 7$ & $n_5=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative calendar categorizations with hourly time index}
\label{definitions}
\end{table}

We start with the definition of an equivalence class and then move on to define a circular granularity.

@@

**Definition:** A **aperiodic circular granularity** can not be defined in terms of modular arithmetic since each coarser unit is not always made up of equal number of finer units.

@@

<!-- Often sets come equipped with a natural hierarchical structure.  For example, the set of natural numbers N is equipped with a natural pre-order structure, where $n\leq n'$ whenever we can find some other number m so that $n+m=n'$. Similarly, -->

<!-- What is multiple and single order granularities -->
The hierarchical structure of time creates a natural nested ordering, where hours are nested within days, days within weeks, weeks within months, and so on. We refer to granularities which are nested within multiple levels as "multiple-order-up" granularities. For example, hour of the week and second of the hour are both multiple-order-up, while hour of the day and second of the minute are single-order-up.

In section \@ref(cirgran-def), the definition of calendar categorisation considers index set as set of integers to be able to perform the modular operations. However, the index of a tsibble can be any date-time object which comes in different formats. [@Grolemund2011-qf] goes a long way in facilitating analysis of date-time data. It not only helps to identify and parse different date-time data, it also helps to extract each date-time element with its own accessor function. However, table 5 shows that it mostly allows for the creation of some calendar categorizations, usually single-order-up.

##Reproduce Table 5 from the paper

@@

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = FALSE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE}
# read_chunk('scripts/main.R')
```

```{r load}

```

@@

For example, suppose the time index is in minutes, and let $n_i$ be the number of categories created by the circular granularity $C_i$. Then the following categorizations can be computed.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
MOH: & $C_1(s)$ & $= s \mod 60$ & $n_1 =$&$60$ \\
MOD: & $C_2(s)$ & $= s \mod `r 60*24`$ & $n_2=$&$`r 60*24`$\\

HOD: & $C_4(s)$ & $= \lfloor s/60\rfloor\mod 24$  & $n_4 =$&$24$ \\
HOW: & $C_6(s)$ & $= \lfloor s/60\rfloor\mod 24*7$  & $n_5=$&$`r 24*7`$\\

DOW: & $C_7(s)$ & $= \lfloor s/24*60\rfloor \mod 7$ & $n_6=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative circular granularities with time index in minutes}
\label{definitions}
\end{table}

It is easy to note here that due to unequal length of months or years, these formulae can not be used for computing week-of-month or day-of-quarter. Thus, we start with the definition of circular granularity and then move on to computing aperiodic granularities.

@@

@@

<!-- What is multiple and single order up granularities -->
The hierarchical structure of time creates a natural nested ordering, where hours are nested within days, days within weeks, weeks within months, and so on. We refer to granularities which are nested within multiple levels as "multiple-order-up" granularities. For example, hour of the week and second of the hour are both multiple-order-up, while hour of the day and second of the minute are single-order-up.

The index of a tsibble can be any date-time object which comes in different formats. [@Grolemund2011-qf] goes a long way in facilitating analysis of date-time data and extracting each date-time element with its own accessor function. However, table shows that it mostly allows for the creation of single-order-up granularities.

```{r table_accessor}
kable(tibble::tibble(
  `Categorisation` = c("Second-of-minute", "Minute-of-hour", "Hour-of-day", "Day-of-week", "Day-of-month", "Week-of-year", "Day-of-year","Month-of-year"),
 Type = c("Periodic", "Periodic", "Periodic", "Periodic", "Aperiodic", "Aperiodic", "Aperiodic", "Periodic"),
Accessor = c("second()", "minute()", "hour()","wday()", "mday()","week()", "yday()", "month()")), format = "latex", booktabs = TRUE)
```

Hence, the idea is to create multiple-order-granularities from single-order-up in order to incorporate and be able to access different calendar categorisation. The computation of multiple-order-up granularities from single-order-up granularities can differ if single-order-up granularities are circular or aperiodic.

### All single-order-up granularities are periodic:

<!-- In section \@ref(cirgran-def), the definition of calendar categorisation considers index set as set of integers to be able to perform the modular operations. However, -->

@@

### Single-order-up granularities are mixed - that is circular or periodic:
